API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
As it was, this sentence gave little information
Grammar

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives and goals for
a \sklearn 1.0 release.
We summarize and conclude in section~\ref{sec:conclusions}.

@@

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets are represented as NumPy arrays or SciPy sparse matrices.
       Hyper-parameter names and values are represented as standard
       Python strings or numbers whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parametrized on other algorithms.
       Whenever feasible, such algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives and goals for
a \sklearn 1.0 release.
We conclude by summarizing the major points of this paper in
section~\ref{sec:conclusions}.

@@

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be represented using custom classes.
       Datasets are represented as NumPy arrays or SciPy sparse matrices.
       Hyper-parameter names and values are represented as standard
       Python strings or numbers whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parametrized on other algorithms.
       Whenever feasible, such algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
